Fixing Vulnerabilities Hinders Maintainability

### 2019-02-05 paper/ICPC19/icpc19.tex
polishing
fix
meaning of M(v)

We compute the mean average of the maintainability score $M(v)$ as follows:

@@

\noindent
where $G$ is the group of maintainability guidelines from BCH
(Table~\ref{tab:guidelines}) and $v$ is the version of the software under
evaluation. The maintenance $M$ based on the guideline $g$ for a given version
of a project is computed with the following equation:

>>>>

Given the violations for the BCH guidelines, we compute the maintainability score
$M(v)$ as follows:

@@

\noindent
where $G$ is the group of maintainability guidelines from BCH
(Table~\ref{tab:guidelines}) and $v$ is the version of the software under
evaluation. $M(v) < 0$ indicates that version $v$ violates the guidelines,
while $M(v) > 0$ indicates that version $v$ follows the BCH guideliens.

The maintenance for the guideline $g$, $M_g$ for a given version
of a project is computed with the following equation:
